\newpage
\addcontentsline{toc}{chapter}{Список использованной литературы}

\begin{thebibliography}{9}
  \bibitem{lee_seung} Daniel D. Lee , H. Sebastian Seung, Algorithms for non-negative matrix factorization, Proceedings of the 13th International Conference on Neural Information Processing Systems, January 01, 2000, Denver, CO
  \bibitem{berry} Michael W. Berry, Murray Browne, Amy N. Langville, V. Paul Pauca, Robert J. Plemmons, Algorithms and applications for approximate nonnegative matrix factorization, Computational Statistics; Data Analysis, Volume 52, Issue 1, 2007.
  \bibitem{elden} Lars Eldén. 2007. Matrix Methods in Data Mining and Pattern Recognition (Fundamentals of Algorithms). Soc. for Industrial and Applied Math., Philadelphia, PA, USA.
  \bibitem{demmel} Деммель Дж. Вычислительная линейная алгебра. М.: Мир, 2001.
  \bibitem{habr} Интернет ресурс 'Habr'. https://habr.com/ru/post/264375/
  \bibitem{vavaris} Vavasis, S.A.: On the complexity of nonnegative matrix factorization. SIAM J. Optim. 20(3) (2009)
  \bibitem{lin} Lin, C.-J., 2005b. Projected gradient methods for non-negative matrix factorization. Tech. Rep. Information and Support Services Technical Report ISSTECH-95-013, Department of Computer Science, National Taiwan University.
  \bibitem{langville} Langville, A., Meyer, C., Albright, R., Cox, J., Duling, D., 2006. Algorithms, initializations, and convergence for the nonnegative matrix factorization, preprint.
  \bibitem{paatero} Paatero, P., 1997. Least squares formulation of robust non-negative factor analysis. Chemometrics and Intelligent Laboratory Systems 37
  \bibitem{chu} Chu, M., Diele, F., Plemmons, R., Ragni, S., 2004. Optimality, computation, and interpretations of nonnegative matrix factorizations
\end{thebibliography}
